### 2020-03-06 short.body.tex
tweak

Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 2 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) caused by symptomatic individuals drive the transmission during the growth phase (Figure~\ref{fig.relevance}A).
On the other hand, assuming a wide generation-interval distribution (higher $\kappa_a$) for asymptomatic individuals increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases (Figure~\ref{fig.relevance}C).

>>>>

Here, given $1/r=7$ days, $\bar G_s=7$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 2 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) caused by symptomatic individuals drive the transmission during the growth phase (Figure~\ref{fig.relevance}A).
On the other hand, assuming a wide generation-interval distribution (higher $\kappa_a$) for asymptomatic individuals increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases (Figure~\ref{fig.relevance}C).
